---
title: "Data Transformation"
author: "RNepal"
date: "9/16/2019"
output: html_document
---


<!-- This file is provided in Data Analysis with R bootcamp by R Nepal (www.rugnepal.org) -->

## Load library

```{r setup, include = FALSE}
library()
```

## Load Data

```{r}
library(readr)
library(dplyr)
library(tidyr)

gapminder <- read_csv("./data/gapminder.csv")

gapminder

```

## Select - Variables

```{r}
## %>%  <------- Ctrl + Alt + m  (Keyboard shortcut)

country_gdp_year <- gapminder %>% 
 select(year,country,gdpPercap,pop) 

# Displays data, so don't remove them below as well
country_gdp_year
```

# Filter by value

```{r}
gapminder_asia <- gapminder %>%
  filter(continent == "Asia") 

  

gapminder_asia
```


## Your Turn - 01

Display country-wise, annual life expectancy of Europe.

```{r}
lifeexp_year_europe<- gapminder%>%
filter(continent=="Europe")%>%
select(year,country,lifeExp)
  


# displays data
lifeexp_year_europe
```


# Mutate - Add New Variables

```{r}
gapminder_total_gdp <- gapminder %>%
  mutate(gdp =  gdpPercap * pop)

# displays data 
gapminder_total_gdp
```

# Your Turn - 02

Find each countries in Asia with life expectancy in 2007 and rank of country's life expectancy.

```{r}
asia_lifeExp <-gapminder %>%
  filter(continent=="Asia",year==2007)%>%
  mutate(rank = min_rank(lifeExp))
   
  

asia_lifeExp %>% arrange(rank)  
```

# Group By - One or more variable

```{r}
gapminder_group_by <- gapminder %>%
  filter(year == 2007) %>%
  group_by()
  
gapminder_group_by
```

# Arrange - Ascending Order

```{r}
gapminder_asc <- gapminder %>%
  filter(year == 2007) %>%
  arrange(gdpPercap)
  
  
  

gapminder_asc 
```

# Arrange - Descending Order

```{r}
gapminder_asc <- gapminder %>%
  
  
  
  
# displays data
gapminder_asc 
```


# Your Turn - 03

Find countries in Asia with low ranked gdpPercap in 1992

```{r}
asia_gdpPercap_1992 <- gapminder %>%
  filter(continent=="Asia", year == 1992) %>%
  arrange(gdpPercap)
  
  
  

  
  
asia_gdpPercap_1992 
```

# Summarize Data

```{r}
gampinder_sum <- gapminder %>%
  group_by(continent) %>%
  summarise(mean_gdp_per = mean(gdpPercap))
  
  
  

  
gampinder_sum
```


